---
title: "Emotional Granularity - All Studies EDA"
author: "Aaron Wright [`aawva@mit.edu`]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
execute:
  eval: false
format:
  html:
    css: styles/quarto_styles.css
  pdf:
    template: styles/quarto_styles.tex
---

<!-- METADATA -->

## Overview

This .qmd is a scratchpad for replicating the Hoemann 2023 analyses. Each study is housed in a separate .qmd. This file is intended to provide a general environment for inspecting data, recording notes, and describing high-level steps taken in the replication process.

<!-- SCRIPT -->

# Exploratory Data Analysis

## Environment

```{text, dependencies}
# install packages
renv::install("tidyverse")
renv::install("here")

# update renv
renv::snapshot()
```

```{r, environment}
library(tidyverse)
library(here)
library(readxl)
```

## Data

This is a study-general survey of the available data.

EDM :

ESM : 
```{r}
# study 1 -
s1_EOD_ratings_by_valence <- read_excel(here("Data", "dataSet1_EOD_rating data_by valence.xlsx"))
s1_EOD_ratings <- read_excel(here("Data", "dataSet1_EOD_rating data.xlsx"))
s1_words <- read_csv(here("Data", "dataSet1_words.csv"))

# study 2 -
s2_ESM_ratings <- read_excel(here("Data", "dataSet2_ESM_rating data.xlsx"))
s2_words <- read_csv(here("Data", "dataSet2_words.csv"))

# study 3 -
s3_ESM_ratings <- read_excel(here("Data", "dataSet3_ESM_rating data.xlsx"))
s3_words <- read_csv(here("Data", "dataSet3_words.csv"))
```

Meta-analytic results

```{r}
meta_positive <- read_csv(here("Data", "meta-analysis_pos.csv"))
meta_negative <- read_csv(here("Data", "meta-analysis_neg.csv"))
```
